Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-09-16 paper/paper.tex
Added correlation plots to paper and accompanying data git, removed boxplots from paper Tested everything on quipu.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/box-plot_D}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-exact/plots/box-plot_D}
  \caption{A comparison of our box plots that show the similarity
    between the stadium shapes simulated stochastically and
    deterministically.  Both show regular oscillatory maxima with
    similar periods.  This is in contrast to our boxpplot comparison
    of one of the Mannik shapes in Figure~\ref{box-mannik}}
  \label{box-stadium}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/box-plot_D}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
  \caption{A comparison of our box plots that show a disparity between
    the behavoir of the stochastic and deterministic simulations in
    our Mannik cells.  The deterministic show a regular, robust
    oscillatory behavoir between the two ends of the cell. The
    stochastic simulation do show a general back and forth tendency
    between two ends of the cell, but it is not robust and tends to
    break down.}
  \label{box-mannik}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/box-plot_D}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-exact/plots/box-plot_D}
  \caption{A comparison of our box plots that show a disparity between
    the behavoir of the stochastic and deterministic simulations in
    our Mannik cells.  The deterministic show a regular, robust
    oscillatory behavoir between the two ends of the cell. The
    stochastic simulation do show a general back and forth tendency
    between two ends of the cell, but it is not robust and tends to
    break down.}
  \label{box-mannik}
\end{figure}

@@

@@

\section{Conclusion}
No conclusion :(
\bibliography{paper}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation-rl.pdf}
  \caption{No caption}
  \label{corr-pill}
\end{figure}

@@

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/box-plot_D}
%%   \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-exact/plots/box-plot_D}
%%   \caption{A comparison of our box plots that show the similarity
%%     between the stadium shapes simulated stochastically and
%%     deterministically.  Both show regular oscillatory maxima with
%%     similar periods.  This is in contrast to our boxpplot comparison
%%     of one of the Mannik shapes in Figure~\ref{box-mannik}}
%%   \label{box-stadium}
%% \end{figure}

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/box-plot_D}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
%%   \caption{A comparison of our box plots that show a disparity between
%%     the behavoir of the stochastic and deterministic simulations in
%%     our Mannik cells.  The deterministic show a regular, robust
%%     oscillatory behavoir between the two ends of the cell. The
%%     stochastic simulation do show a general back and forth tendency
%%     between two ends of the cell, but it is not robust and tends to
%%     break down.}
%%   \label{box-mannik}
%% \end{figure}
%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/box-plot_D}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-exact/plots/box-plot_D}
%%   \caption{A comparison of our box plots that show a disparity between
%%     the behavoir of the stochastic and deterministic simulations in
%%     our Mannik cells.  The deterministic show a regular, robust
%%     oscillatory behavoir between the two ends of the cell. The
%%     stochastic simulation do show a general back and forth tendency
%%     between two ends of the cell, but it is not robust and tends to
%%     break down.}
%%   \label{box-mannik}
%% \end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation-rl.pdf}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation-rl.pdf}
  \caption{Correlation for A shapes}
  \label{corr-A}
\end{figure}

@@

\section{Conclusion}
No conclusion :(
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/correlation-rl.pdf}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_92-1_18-0_00-15_00-full_array/plots/correlation-rl.pdf}
  \caption{Correlation for B shapes}
  \label{corr-B}
\end{figure}

\bibliography{paper}
